\documentclass{exam}
\usepackage[utf8]{inputenc}
\title{IEEE ML-Club Meeting-1} 
\author{Jaley Dholakiya,Sumit Jha}
\begin{document}
\maketitle
\begin{center}
\fbox{\fbox{\parbox{5.5in}{\centering
Dont write anything in blank spaces. Only scribble or draw visualizations in a way that helps you remember}}}
\end{center}
 
\vspace{5mm}
 
\makebox[\textwidth]{Name :\enspace\hrulefill}
 
 
\begin{questions}
\question Define Machine Learning. Write top three python packages to try out.
\vspace{\stretch{1}}
\question Plot the people attending "Music Award Program" with the features being salary on x-axis and following on y-axis.
\vspace{\stretch{1}}

\question What is soo \textbf{"super"} in Supervised Learning? Why is semi-supervised learning perfect fit for mining web? 
\vspace{\stretch{1}}
\question What is \textbf{post}erior probability in spam non-spam classifier? Mark it in the bellow Equation.
\begin{equation}
P(email=spam|emails-bow)\propto P(emails-bow|email=spam)*P(spam)
\end{equation}
\vspace{\stretch{1}}

\clearpage
%------------------------------------------------
\question What is cost Function and the gradient in Regression problem?
\vspace{\stretch{1}}
\question Can you visualize regression problem in two different spaces? Co-ordinate space and Parametric Space? Can you think of it for classification problem too?
\vspace{\stretch{1}}
\question Why is gradient-descent algorithm called fulcrum for most of the learning algorithms.
\vspace{\stretch{1}}
\question How do you smell overfitting in learning problem? What are the possible solutions? What is train-test split? What is n-fold validation?
\vspace{\stretch{1}}
\question Describe precision, Recall, Accuracy seperately.(Homework Question)
\vspace{\stretch{1}}


\question What is AI Winter? How did Neural Networks survive it? What makes deep learning different from neural networks?
\vspace{\stretch{1}}


\clearpage
%------------------------------------------------


\question What is symbolic evaluation? And how is it different from normal evaluation?
\vspace{\stretch{1}}
\question What is Tensor in Tensorflow? How is constant Variable different from placeholder variable in tensorflow?
\vspace{\stretch{1}}
\question What is a session in tensorflow? What does optimizer in tensorflow do? Is the optimizer facilitating forward evaluation or backward update?
\vspace{\stretch{1}}
\question How does Keras perfectly complement Tensorflow?
\vspace{\stretch{1}}

\clearpage
%------------------------------------------------





\end{questions} 
\end{document}